Variational Inference for Inverse Reinforcement Learning with Gaussian Processes

### 2018-12-06 mprop/mprop.tex
Proofs of the helper theorems

Following previous work on GP IRL
\cite{DBLP:conf/nips/LevinePK11,DBLP:conf/uai/JinDAS17}, we use a maximum
entropy IRL model \cite{ziebart2008maximum}, under which we have that
\[ P(a | s) \propto \exp(Q_r(s, a)), \]
where
\begin{equation}
  Q_r(s, a) = r(s) + \gamma\sum_{s' \in \mathcal{S}}
  \mathcal{T}(s, a, s')V_r(s'),
\end{equation}
and $V_r(s)$ is a `soft' version of the Bellman backup operator, which can be
obtained by repeatedly applying the following equation until convergence:
\cite{DBLP:conf/nips/LevinePK11,supplementary_material}
\[ V_r(s) = \log \sum_{a \in \mathcal{A}} \exp\left( r(s) + \gamma\sum_{s' \in
      \mathcal{S}} \mathcal{T}(s, a, s')V_r(s') \right). \]
The likelihood of the data can then be written down as
\cite{DBLP:conf/uai/JinDAS17,DBLP:conf/nips/LevinePK11}
\begin{equation} \label{pDr}
  p(\mathcal{D} | r) = \prod_{i=1}^N \prod_{t=1}^T p(a_{i,t} | s_{i,t}) = \exp\left( \sum_{i=1}^N \sum_{t=1}^T Q_r(s_{i,t}, a_{i,t}) - V_r(s_{i,t}) \right).
\end{equation}
However, a reward function learned by maximising this likelihood is not
transferable to new situations
\cite{DBLP:conf/uai/JinDAS17,DBLP:conf/nips/LevinePK11}. One needs to model the
reward structure in a way that would allow reward predictions for previously
unseen states.

>>>>

Following previous work on GP IRL
\cite{DBLP:conf/nips/LevinePK11,DBLP:conf/uai/JinDAS17}, we use a maximum
entropy IRL model \cite{ziebart2008maximum}, under which we have that
\[ P(a | s) \propto \exp(Q_r(s, a)), \]
where
\begin{equation}
  Q_r(s, a) = r(s) + \gamma\sum_{s' \in \mathcal{S}}
  \mathcal{T}(s, a, s')V_r(s'),
\end{equation} % TODO: fix the wording!!!
and $V_r(s)$ is a `soft' version of the Bellman backup operator, which can be
obtained by repeatedly applying the following equation until convergence:
\cite{DBLP:conf/nips/LevinePK11,supplementary_material}
\[ V_r(s) = \log \sum_{a \in \mathcal{A}} \exp\left( r(s) + \gamma\sum_{s' \in
      \mathcal{S}} \mathcal{T}(s, a, s')V_r(s') \right). \]
The likelihood of the data can then be written down as
\cite{DBLP:conf/uai/JinDAS17,DBLP:conf/nips/LevinePK11}
\begin{equation} \label{pDr}
  p(\mathcal{D} | r) = \prod_{i=1}^N \prod_{t=1}^T p(a_{i,t} | s_{i,t}) = \exp\left( \sum_{i=1}^N \sum_{t=1}^T Q_r(s_{i,t}, a_{i,t}) - V_r(s_{i,t}) \right).
\end{equation}
However, a reward function learned by maximising this likelihood is not
transferable to new situations
\cite{DBLP:conf/uai/JinDAS17,DBLP:conf/nips/LevinePK11}. One needs to model the
reward structure in a way that would allow reward predictions for previously
unseen states.
